---
title       : Shiny Application on mtcars dataset
subtitle    : The relationship between variables and miles per gallon (MPG)
author      : Santhoshi Dharmireddi
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : standalone # {standalone, draft}
knit        : slidify::knit2slides
ext_widgets: {rCharts: [libraries/nvd3]}
---

## Introduction:

This presentation is part of the Course Project for the Developing Data Products class. The peer assessed assignment has two parts. First, we need to create a Shiny application and deploy it on Rsrudio's servers. Second, we should use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about the application. This presentation addresses the second part of the course project.

The app developed for the first part of the assignment is available at:

https://santhoshidharmireddi.shinyapps.io/DDPCourseProject

Source code for ui.R and server.R files are available on the Github:

https://github.com/santhoshidharmireddy/Developing-Data-Products-Project/tree/master/CourseProjectPart1



--- .class #id 

## Design

The application uses the default "mtcars" dataset installed with R. It contains plot settings for interactive data analysis without much code modifications.

This app helps you to find the relationship between different variables and miles per gallon (MPG). This app also provides summary statistics for each relationship.



--- .class #id 

## mtcars Dataset

The data used in the app comes from the Motor Trend Car Road Tests (mtcars) dataset. The data was extracted from the 1974 Motor Trend US magazine, and comprise fuel consumption and 10 variables of automobile design and performance for 32 automobiles (1973-74 models). We can look at some characteristics of the data:

```{r}
head(mtcars)
```


--- .class #id

## Plot

```{r, echo=TRUE,out.height="400px",out.width="600px"}
formula<- lm(mpg ~ cyl, data = mtcars)
p<- plot(as.integer(mtcars$cyl), mtcars$mpg, xlab = "cyl", ylab = "mpg")
abline(formula, col=2)

```

